### 2020-08-06 paper.tex
Final Draft
Move Previous Efforts

\newcommand{\version}{v0.4 Draft}

@@

We will conclude this introductory section with the clarification of important terms. Section~\ref{sec:interviews} presents the interview results along with the collected war story reports. Before we validate them in an observational study in Section~\ref{sec:study}, we will have a look at current and previous research regarding the debugging of RAs in Section~\ref{sec:discussion}. We will finally answer RQ2 in Section~\ref{sec:future} ``Future Work''.

>>>>

\newcommand{\version}{v0.9 Final Draft}

@@

We will conclude this introductory section with the clarification of important terms. Section~\ref{sec:interviews} presents the interview results along with the collected war story reports. After we validate them in an observational study in Section~\ref{sec:study}, we will have a look at current and previous research regarding the debugging of RAs in Section~\ref{sec:discussion}. We will finally answer RQ2 in Section~\ref{sec:future} ``Future Work''.
